---
title: "R Notebook"
output: html_notebook
---

## orange juice

The weekly sales data of refrigerated 64-ounce orange juice
containers from 83 stores in the Chicago area. There are many stores throughout the city, many time periods, and also three different brands (Dominicks, MinuteMaid,and Tropicana). 

The data are arranged in rows, with each row giving the recorded
store sales (in logarithms; logmove), as well as brand, price, presence/absence of feature advertisement, and the demographic characteristics of the store.
There are 28,947 rows in this data set. The data is taken from P. Rossi’s bayesm package for R, and it has been used earlier in Montgomery (1987).

### Library list

```{r}

library(lattice)



```

### The orange juice data

```{r}

oj <- read.csv("csv/oj.csv")

oj$store <- as.factor(oj$store)

```

#### View the data

```{r}

head(oj)

str(oj)

summary(oj)

```

### Analysing the brand

```{r}

table(oj$brand)

aggregate()

```
























































